Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-04-29 concurrency/CONCUR 2023/paper.tex
try with annotated code

\authorrunning{Duc Than Nguyen et al.} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

@@

@@

\begin{figure}[h]
	\centering
	\begin{mathpar}
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\ \texttt{pn->n->t}  
			\end{array}
			\right\}
		}
		\\ 
		\texttt{insertOp(pn, k, v)} 
		\\
		{\color{blue}
			\left\{\exists \  \texttt{t' l r lk1 lk2}.
			\begin{array}{c}
				\ \texttt{pn->n->t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \ \ast \ \\ 
				\ \texttt{l} \mapsto \texttt{(NULL, lk1)}\  \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2)}
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specification of \texttt{insertOp} for the lock-coupling template}
	\label{fig:insertOp_lock}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{mathpar}
		%insertOp for give-up
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t} \  \ast \ \texttt{n}\mapsto\texttt{min} \ \ast \ \texttt{n}\mapsto\texttt{max}
			\end{array}
			\right\}
		}
		\\
		\texttt{insertOp(pn, k, v)}
		\\
		{\color{blue}
			\left\{\exists \ \texttt{t' l r lk1 lk2}. 
			\begin{array}{c}
				\ \texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \\ 
				\ \ast \ \texttt{l} \mapsto \texttt{(NULL, lk1, (min, k))} \ \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2, (k, max))}
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specifications of \texttt{inRange} and \texttt{insertOp} for the give-up template}
	\label{fig:insertOp_giveup}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% inRange for give-up
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn->n}\mapsto\texttt{(t, lock, min, max)} 
			\end{array}
			\right\}
		}
		\\ 
		\texttt{inRange(pn, k)} 
		\\
		{\color{blue}
			\left\{\texttt{res.} \
			\begin{array}{c}
				\ \texttt{pn->n}\mapsto\texttt{(t, lock, min, max)} \  \\ 
				\ \ast  \ \texttt{(if res then } \texttt{(min < k < max)} \texttt{ else } \texttt{(k} \leq \texttt{min} \lor \texttt{k} \geq \texttt{max))}
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specifications of \texttt{inRange} and \texttt{insertOp} for the give-up template}
	\label{fig:inRange_giveup}
\end{figure}

>>>>

\authorrunning{Duc Than Nguyen, Lennart Beringer,  William Mansky, and Shengyi Wang} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

@@

\newcommand\lstsetnumber[1]{\gdef\thelstnumber{#1}}
\begin{figure}[ht]
	$\color{blue}\left\langle\begin{array}{l} \nodeboxrep(b,g\_root)\ *\ \mathsf{atomic\_shift}(P_p,E_i,E_o,Q_p,Q)\end{array}\right\rangle$
	\begin{lstlisting}[language = C, style=myStyle, mathescape=true]
		int traverse(pn *pn, int k){
			  int flag = 1; 			$\left\{\begin{array}{l} 		\ghost{\mathsf{my\_half}((-\infty,+\infty),info)}{g\_root}\ *\ R\ b\ *\ \mathsf{lock\_inv}(l,lsh2,R')\ *\ \\
			  	\nodeboxrep(b,g\_root)\ *\ \mathsf{atomic\_shift}(P_p,E_i,E_o,Q_p,Q)\end{array}\right\} \Rrightarrow \left\{\begin{array}{l} lookup\_inv \end{array}\right\}$
		  		for( ; ; ){ 			$\left\{\begin{array}{l} lookup\_inv \end{array}\right\} \triangleq \left\{\begin{array}{l}(x\in range)\land \ghost{\mathsf{my\_half}(range,info)}{g\_current}*\ R\ np\ *\\\mathsf{lock\_inv}(lock,lsh2,R')\ *\ \nodeboxrep(b,g\_root)\ *\ \mathsf{atomic\_shift}(P_p,E_i,E_o,Q_p,Q)\end{array}\right\}$
		  			pn->p = pn->n;
		  			if (pn->p->t == NULL)
		  					break;
		  			else{
		  					int b = findNext(pn, k);
		  					if (b == 0){
		  							flag = 0;
		  							break;
		  					}
		  					else{
		  						acquire(pn->n->lock);
		  						release(pn->p->lock);
		  					}
		  				}
	  				}
  				return flag;
  		}  $\lstsetnumber{}$\end{lstlisting}
$\color{blue}\left\langle\begin{array}{l} \nodeboxrep(b,g\_root)\ *\ \mathsf{atomic\_shift}(P_p,E_i,E_o,Q_p,Q)\end{array}\right\rangle$
\caption{proof of \texttt{traverse}}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}{\textwidth}
	\centering
	\begin{mathpar}
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\ \texttt{pn->n->t}  
			\end{array}
			\right\}
		}
		\\ 
		\texttt{insertOp(pn, k, v)} 
		\\
		{\color{blue}
			\left\{\exists \  \texttt{t' l r lk1 lk2}.
			\begin{array}{c}
				\ \texttt{pn->n->t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \ \ast \ \\ 
				\ \texttt{l} \mapsto \texttt{(NULL, lk1)}\  \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2)}
			\end{array}
			\right\}
		}
		\end{mathpar}
		\caption{Specification of \texttt{insertOp} for the lock-coupling template}
			\label{fig:insertOp_lock}
	\end{subfigure}
	%insertOp for give-up of give-up
	\begin{subfigure}{\textwidth}
		\begin{mathpar}
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t} \  \ast \ \texttt{n}\mapsto\texttt{min} \ \ast \ \texttt{n}\mapsto\texttt{max}
		\end{array}
		\right\}
	}
	\\
	\texttt{insertOp(pn, k, v)}
	\\
	{\color{blue}
		\left\{\exists \ \texttt{t' l r lk1 lk2}. 
		\begin{array}{c}
			\ \texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \\ 
			\ \ast \ \texttt{l} \mapsto \texttt{(NULL, lk1, (min, k))} \ \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2, (k, max))}
		\end{array}
		\right\}
	}
	\end{mathpar}
	\caption{Specification of \texttt{insertOp} for the give-up template}
	\label{fig:insertOp_giveup}
\end{subfigure}
	\caption{Specification of \texttt{insertOp} for the lock-coupling template}
	\label{fig:insertOp}
\end{figure}

@@

@@

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% inRange for give-up
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn->n}\mapsto\texttt{(t, lock, min, max)} 
			\end{array}
			\right\}
		}
		\\ 
		\texttt{inRange(pn, k)} 
		\\
		{\color{blue}
			\left\{\texttt{res.} \
			\begin{array}{c}
				\ \texttt{pn->n}\mapsto\texttt{(t, lock, min, max)} \  \ast  \ 
				\\ \texttt{(if res then } \texttt{(min < k < max)} \texttt{ else } \texttt{(k} \leq \texttt{min} \lor \texttt{k} \geq \texttt{max))}
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specifications of \texttt{inRange} and \texttt{insertOp} for the give-up template}
	\label{fig:inRange_giveup}
\end{figure}
